---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis build status](https://travis-ci.org/jrosen48/railtrails.svg?branch=master)](https://travis-ci.org/jrosen48/railtrails)

# railtrails

This R data package provides rail information about [rail trails](https://en.wikipedia.org/wiki/Rail_trail) from the excellent [TrailLink](https://www.traillink.com/) website, sponsored by the Rails-to-Trails Conservancy. Includes information (such as name, length, surface, and reviews) 3,846 trails in every state in the United States.

## Installation

You can install railtrails with the `install.packages()` function.

```{r gh-installation, eval = FALSE}
install.packages("railtrails")
```

## Loading the data

Here is how to load the data:

```{r example}
d <- railtrails::railtrails
d
```

## "Unnesting" trail reviews

You may want to "unnest" the list-column with reviews in the following way:

```{r, unnesting}
library(tidyr)
d <- railtrails::railtrails
d <- d %>% unnest(raw_reviews)
d
```

## Shiny App

An interactive web application (Shiny) for finding the top-rated trails in each state is available [here](https://jmichaelrosenberg.shinyapps.io/railtrails/). The source code is in the [app](/app) directory.

## Notes

* See more information about the variables with `?railtrails`

* If you like using this package, please consider visiting or even making a donation to the Rails to Trails Conservancy at via https://www.traillink.com/

* The data was last updated 2018/2/2

* Contributions are welcome. Pull requests and requests for features can be made on GitHub

* Thank you to [Bob Rudis](https://rud.is/) for feedback that helped to improve this package

## Code of conduct

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
