---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# railtrails

This R data package provides rail information  about [rail trails](https://en.wikipedia.org/wiki/Rail_trail) from the excellent [TrailLink](https://www.traillink.com/) website, sponsored by the Rails-to-Trails Conservancy. 

## Installation

You can install railtrails from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jrosen48/railtrail")
```

## Loading the rail-trails data

Here is how to load the data:

```{r example}
railtrails::railtrails
```

You may want to "unnest" the last column with reviews, as follows:

```{r}
library(tidyr)
railtrails <- railtrails %>% unnest(raw_reviews)
railtrails
```

## Note

I checked whether they had a way to access the reviews on the site through an API. They didn't, so I checked their `robots.txt` file at `http://traillink.com/robots.txt`. They didn't disallow access to their trail pages or the pages listing trails for each state. Additionally, I checked their terms of service, which did not prohibit accessing their data in this way, and so I proceeded to scrape this data using a reasonable delay in between page requests in order to not over-burden their server.
