---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis build status](https://travis-ci.org/jrosen48/railtrails.svg?branch=master)](https://travis-ci.org/jrosen48/railtrails) [![CRAN status](http://www.r-pkg.org/badges/version/railtrails)](https://cran.r-project.org/package=railtrails)

# railtrails

This R data package provides rail information about [rail trails](https://en.wikipedia.org/wiki/Rail_trail) from the excellent [TrailLink](https://www.traillink.com/) website, sponsored by the Rails-to-Trails Conservancy. Includes information (such as name, length, surface, and reviews) 3,846 trails and 24,413 reviews in every state in the United States.

## Installation

You can install railtrails with the `install.packages()` function.

```{r gh-installation, eval = FALSE}
install.packages("railtrails")
```

## Loading the data

Here is how to load the data:

```{r example}
d <- railtrails::railtrails
d
```

## "Unnesting" trail reviews

You may want to "unnest" the list-column with reviews in the following way:

```{r, unnesting}
library(tidyr)
d <- railtrails::railtrails
d <- d %>% unnest(raw_reviews)
d
```

## Notes

See more information about the variables with `?railtrails`.

If you like using this package, please consider visiting or even making a donation to the Rails to Trails Conservancy at via https://www.traillink.com/.

The data was last updated 2018/2/2.

## Future improvements

I am interested in adding the trailhead location to the data; this can be done fairly easily using the Google Maps API but will take considerable time due to the number of trails. Contributions are welcome. Requests for features can be made [on GitHub](https://github.com/jrosen48/railtrails/issues).

## Acknowledgment

Thank you to [Bob Rudis](https://rud.is/) for feedback that helped to improve this package.

## Code of conduct

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
  
